---
title: "MEAD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MEAD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We give a tutorial on how to use MEAD in this vignette.

## Install the package

```{r setup,eval=FALSE}
install.packages('devtools')
devtools::install_github('DongyueXie/MEAD')
library(MEAD)
```


## Load data

Neuron dataset from [Jerber et al. (2021)](https://www.nature.com/articles/s41588-021-00801-6). We selected 6 individuals as reference and bulk samples are obtained by aggregating single cell data.

```{r}
ref = readRDS('ref.rds')
bulk = readRDS('bulk.rds')
```

## Run analysis

Run MEAD

```{r}
# R01 = get_R01(bulk,alpha=0.1)
# To get R01, uncomment the above line and comment out the next line.
R01 = readRDS('R01.rds')
fit = MEAD(bulk[,1:10],ref,R01=R01)
```

Estimated cell type proportions.

```{r}
t(fit$p_hat)
```

Standard errors of estimated cell type proportions.

```{r}
t(fit$p_hat_se)
```

Construct confidence intervals of proportions.

```{r}
get_ci(fit)
```
